---
title: 'Regression Models: Practice'
author: "Marcio Gualtieri"
output:
  html_notebook:
    css: ./styles/style.css
    toc: yes
    toc_depth: 4
  html_document:
    css: ./styles/style.css
    toc: yes
    toc_depth: 4
  pdf_document:
    toc: yes
    toc_depth: '4'
---

# Installing the Required Packages

You might need to install the following packages if you don't already have them:

```{r, eval = FALSE}
install.packages("xtable")
install.packages("Amelia")
```

Just uncomment the packages you need and run this chunk before you run the remaining ones in this notebook.

# Importing the Required Packages

Once the libraries are installed, you need to load them as follows:

```{r}
suppressMessages(library(xtable))   # Pretty printing dataframes
suppressMessages(library(Amelia))   # Missing data
suppressMessages(library(graphics))
```

# Loading the Data-set

```{r}
company_data <- read.csv('_cf0fd3361e05f5be5304b07b771bad48_companydata.csv',
                         na.strings=c("NA", "NULL", ""), stringsAsFactors = F)
```

Let's take a sample:

```{r, results="asis"}
render_table_in_viewer_pane <- function(data) {
  html <- print(xtable(data), type = "html", print.results=FALSE)
  temp <- tempfile(fileext = ".html")
  cat(html, file = temp)
  rstudioapi::viewer(temp)
}

render_table <- function(data) {
  render_table_in_viewer_pane(data)
  print(xtable(data), type = "html")
}

sample_data_frame <- function(data, size) {
  sample_index <- sample(1:nrow(data), size)
  return(data[sample_index, ])
}

render_table(sample_data_frame(company_data, 12))
```

## Data Types

```{r}
str(company_data)
```

## Missing Data

```{r}
missmap(company_data, main = "Missing Values", col = c("red", "lightgrey"))
```

The data-set seems complete (no `NA`s or `NULL`s).

# Relationship Between `y` and `x1`

1. [It has been widely noted that there is a relationship between x1 and y.] We are interested in studying the magnitude of this relationship and reporting results to the president of the company.

## Exploratory Data Analysis

```{r}
pairs(company_data, panel = panel.smooth, main = "Company Data", col = "light blue") 
``` 

## Fitting a Model for `y` and `x1`

Let's fit a linear model first:

```{r}
fit <- lm(y ~ x1, data = company_data)
```

The plot for the fitted model is the following:

```{r}
plot(company_data$x1, company_data$y,  
     xlab = "x1", ylab = "y", 
     bg = "lightblue", 
     col = "black", cex = 1.1, pch = 21, frame = FALSE)
abline(fit, lwd = 2)
```

It seems that there is a linear correlation between the variables `x1` and `y`, but also between the pairs (`x2`, `y`), (`x1`, `x2`) and (`x1`, `x2`). Given that (`x1`, `x2`) seem correlated, without any information about what these variables represent, there's no way to tell if there is a meaningful relationship between (`y`, `x1`). Could actually be a meaninful relationship between (`x2`, `y`) or some other variable not included in the data-set paired with `y`.


# Coefficient for `x1`

2. Report the estimated coefficient for x1 from your model to 6 significant digits.

```{r}
summary(fit)
```

Specifically, the coefficient of `x1` is:

```{r}
coefficients(fit)[2]
```

# Confidence Interval

3. Report the 95% confidence interval for the coefficient for x1 from your model. Use 6 significant digits for both the lower and upper bounds. Report it in the format (Lower Bound, Upper Bound)

```{r}
coefs <- summary(fit)$coefficients

x1Coefs <- coefs[2, ]

x1Estimate <- x1Coefs[1]
x1StandardError <- x1Coefs[2]

x1Estimate + c(-1, 1) * qt(.975, df = fit$df) * x1StandardError
```

# P-Value for `X1`

4. Report the p-value associated with the coefficient for x1 from your model to 6 significant digits. Use scientific notation.

```{r}
x1Coefs[4]
```

